Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-16 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
删除重复表格

\begin{table*}
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|ccccccccccccccccc}
\toprule
Iterations &  0    &  1    &  2    &  4    & 8   & 16  & 32  & 64  & 128 & 256  & 512   & 1024  & 2048  & 4096  & 8192  & 16384 & 32768 \\ \midrule
AO (Fake Trajectory)   & 0.004 & 0.002 &0.002 & 0.002 &0.002&0.002&0.003&0.007&0.042& 0.299& 0.668 & 0.746 & 0.781 & 0.798 & 0.820 & 0.821 & 0.818 \\
SR (FGT) & 0.000 & 0.000 &0.000 & 0.000 &0.000&0.000&0.001&0.005&0.044& 0.335& 0.749 & 0.822 & 0.855 & 0.872 & 0.895 & 0.897 & 0.890 \\ \midrule
AO (GT)    &  0.760& 0.757 &0.756 & 0.757 &0.757&0.758&0.759&0.753&0.720& 0.474& 0.150 & 0.095 & 0.071 & 0.041 & 0.032 & 0.032 & 0.035 \\
SR (GT) &  0.897& 0.894 &0.891 & 0.893 &0.891&0.893&0.896&0.888&0.852& 0.559& 0.164 & 0.098 & 0.066 & 0.031 & 0.021 & 0.022 & 0.023 \\ \midrule
SSIM     &  1.00 & 1.00  & 1.00 & 1.00  &1.00 &0.99 & 0.99& 0.97& 0.93& 0.86 & 0.86  & 0.87  & 0.88  & 0.88  & 0.88  & 0.88  & 0.88  \\
MSE      &  0.00 & 0.51  & 0.26 & 0.32  & 0.37& 0.48& 0.84& 2.03& 5.65&15.10 & 25.43 & 23.70 & 21.89 & 20.69 & 20.49 & 20.03 & 20.87 \\ \bottomrule
\end{tabular}%
}
\caption{Influence of Training Iterations}
\label{tab:iter}
\end{table*}

% \usepackage{multirow}
% \usepackage{booktabs}

\begin{table*}
\centering
\resizebox{\textwidth}{!}{%
\label{tab:iter}
\begin{tabular}{c|c|ccccccccccccccccc} 
\toprule
\multicolumn{2}{c|}{Iterations}  & 0     & 1     & 2     & 4     & 8     & 16    & 32    & 64    & 128   & 256   & 512   & 1024  & 2048  & 4096  & 8192  & 16384 & 32768  \\ 
\midrule
\multirow{2}{*}{Fake Trajectory} & AO   & 0.004 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 & 0.007 & 0.042 & 0.299 & 0.668 & 0.746 & 0.781 & 0.798 & 0.820 & 0.821 & 0.818  \\
                                 & SR   & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.001 & 0.005 & 0.044 & 0.335 & 0.749 & 0.822 & 0.855 & 0.872 & 0.895 & 0.897 & 0.890  \\ 
\midrule
\multirow{2}{*}{Real Trajectory} & AO   & 0.760 & 0.757 & 0.756 & 0.757 & 0.757 & 0.758 & 0.759 & 0.753 & 0.720 & 0.474 & 0.150 & 0.095 & 0.071 & 0.041 & 0.032 & 0.032 & 0.035  \\
                                 & SR   & 0.897 & 0.894 & 0.891 & 0.893 & 0.891 & 0.893 & 0.896 & 0.888 & 0.852 & 0.559 & 0.164 & 0.098 & 0.066 & 0.031 & 0.021 & 0.022 & 0.023  \\ 
\midrule
\multicolumn{2}{c|}{SSIM}                      & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 0.99  & 0.99  & 0.97  & 0.93  & 0.86  & 0.86  & 0.87  & 0.88  & 0.88  & 0.88  & 0.88  & 0.88   \\
\multicolumn{2}{c|}{MSE}                       & 0.00  & 0.51  & 0.26  & 0.32  & 0.37  & 0.48  & 0.84  & 2.03  & 5.65  & 15.10 & 25.43 & 23.70 & 21.89 & 20.69 & 20.49 & 20.03 & 20.87  \\
\bottomrule
\end{tabular}
}
\caption{Influence of Training Iterations}
\end{table*}

>>>>

\begin{table*}
\centering
\resizebox{\textwidth}{!}{%
\label{tab:iter}
\begin{tabular}{cc|ccccccccccccccccc} 
\toprule
\multicolumn{2}{c|}{Iterations}  & 0     & 1     & 2     & 4     & 8     & 16    & 32    & 64    & 128   & 256   & 512   & 1024  & 2048  & 4096  & 8192  & 16384 & 32768  \\ 
\midrule
\multirow{2}{*}{Fake Trajectory} & AO   & 0.004 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 & 0.007 & 0.042 & 0.299 & 0.668 & 0.746 & 0.781 & 0.798 & 0.820 & 0.821 & 0.818  \\
                                 & SR   & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.001 & 0.005 & 0.044 & 0.335 & 0.749 & 0.822 & 0.855 & 0.872 & 0.895 & 0.897 & 0.890  \\ 
\midrule
\multirow{2}{*}{Real Trajectory} & AO   & 0.760 & 0.757 & 0.756 & 0.757 & 0.757 & 0.758 & 0.759 & 0.753 & 0.720 & 0.474 & 0.150 & 0.095 & 0.071 & 0.041 & 0.032 & 0.032 & 0.035  \\
                                 & SR   & 0.897 & 0.894 & 0.891 & 0.893 & 0.891 & 0.893 & 0.896 & 0.888 & 0.852 & 0.559 & 0.164 & 0.098 & 0.066 & 0.031 & 0.021 & 0.022 & 0.023  \\ 
\midrule
\multicolumn{2}{c|}{SSIM}                      & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 0.99  & 0.99  & 0.97  & 0.93  & 0.86  & 0.86  & 0.87  & 0.88  & 0.88  & 0.88  & 0.88  & 0.88   \\
\multicolumn{2}{c|}{MSE}                       & 0.00  & 0.51  & 0.26  & 0.32  & 0.37  & 0.48  & 0.84  & 2.03  & 5.65  & 15.10 & 25.43 & 23.70 & 21.89 & 20.69 & 20.49 & 20.03 & 20.87  \\
\bottomrule
\end{tabular}
}
\caption{Influence of Training Iterations}
\end{table*}
